\chapter{Conclusion}
\label{chap:conclusion}

\section{Summary and Key Findings}

This thesis investigated whether the popularity of Reddit posts can be predicted using semantic text embeddings and structured metadata, and whether such predictions can inform a practical automated posting pipeline. The work examined this question through two complementary lenses: offline cross-validation experiments on historical data, and a live deployment experiment involving model-guided post selection on Reddit.

The offline experiments demonstrated that Reddit post reception is predictable to a moderate extent using publicly available features. The trained XGBoost regression models achieved Spearman correlations exceeding 0.20 across multiple subreddits and mean absolute errors around 7\% when predicting upvote ratio. Semantic embeddings derived from the Stella 400M transformer model contributed substantially to predictive performance, outperforming classical TF-IDF representations and demonstrating that contextual text understanding captures meaningful signal related to community response. Additional structured features—including temporal patterns, author history, domain characteristics, and subreddit-specific metadata—further improved model accuracy. These results indicate that historical Reddit data contains detectable patterns related to post reception, and that such patterns can be extracted using off-the-shelf machine learning tools and publicly available archival data.

However, the live experiment revealed a sharp divergence between offline validation performance and real-world deployment outcomes. Model-approved posts—selected from the top 10\% of predicted upvote ratios—did not outperform randomly selected posts. In fact, model-approved posts achieved lower mean upvote ratios (0.808 vs. 0.872), lower scores, and fewer comments than the random baseline. More critically, predictions showed a strong negative correlation with actual outcomes within the model-approved subset ($\rho = -0.596$, $p < 0.0001$), indicating that the model actively selected posts in the wrong order. This deployment failure cannot be attributed to noise or weak signal alone—it represents a systematic inversion of the learned ranking.

The live experiment also revealed an important asymmetry: while model-guided selection failed, content generation succeeded. Randomly selected generated posts achieved a mean upvote ratio of 0.872, substantially exceeding the historical training baseline of 0.729 calculated from organic user-submitted content. This demonstrates that language models can produce posts that communities do not systematically reject, even when those posts originate from unfamiliar accounts. The primary point of failure was not the generation of plausible content, but the model's inability to predict which generated posts would perform well.

These findings collectively demonstrate that the technical barrier to constructing such a pipeline is low—publicly available data, transformer embeddings, gradient boosting, and generative language models can be combined into a functional system with modest computational resources—but that offline predictive accuracy does not guarantee deployment effectiveness. The gap between historical prediction and live performance points to a fundamental distribution shift: models trained on human-authored posts embedded in natural community dynamics fail when applied to generated content from low-authenticity accounts. This distribution shift may arise from several sources, including spurious correlations in the training data that do not generalize to generated content, differences in how communities respond to posts from unfamiliar versus established users, or systematic differences between historical organic posts and model-generated submissions that the feature representation cannot capture.

The thesis also documented substantial moderation resistance during deployment. Four of nine targeted subreddits banned the posting account, and an additional 17 posts were individually removed across remaining communities. These moderation actions occurred despite the generated content being topically relevant and stylistically similar to organic discussions, suggesting that automated posting faces social and procedural barriers beyond content quality alone. Community members identified the account as suspicious based on posting patterns, lack of comment engagement, and behavioral signals rather than textual content, indicating that successful deployment requires more than optimizing individual post quality.

\section{Limitations}
\label{sec:limitations}

Several limitations constrain the scope and generalizability of these findings.

\textbf{Limited subreddit coverage.} The analysis covers only 19 subreddits, a very small subset of Reddit as a whole. The selected communities are not necessarily representative of the broader platform, and the observed patterns may not generalize to subreddits with different structures, norms, or user populations. Conclusions regarding cross-community generalizability, including the distinction between politically oriented and neutral subreddit groups, should be interpreted cautiously.

\textbf{Dataset filtering and selection bias.} The final dataset retained only 50.2\% of posts from the initial Pushshift collection after applying API availability filters and minimum engagement thresholds. This filtering systematically excludes posts that were deleted, removed by moderators, failed to appear successfully, or received minimal engagement. The training data is therefore biased toward observable and retained posts, which limits conclusions about the full distribution of attempted submissions. Posts removed immediately by automated filters or moderation may not be represented in the archival data at all, meaning the dataset likely excludes certain forms of disallowed or low-quality content before any filtering by this study begins.

\textbf{Text-only posts.} The live experiment generated only self posts (text-based discussion threads), excluding link submissions. While link posts were included in the training data to improve overall model performance, the deployment evaluation focused exclusively on text posts. This limits conclusions about the pipeline's effectiveness for link-based content and may have contributed to distribution shift, as the model was trained on a mixture of post types but applied only to generated text posts.

\textbf{Imperfect prediction target.} Upvote ratio is a useful operationalization of post reception, but it is not a pure measure of quality, relevance, or persuasive success. It reflects a mixture of textual quality, topical fit, community agreement, early vote dynamics, ranking effects, and platform-specific mechanisms. The model may therefore learn patterns associated with observable community response that do not correspond to causal drivers of post quality or effectiveness.

\textbf{Missing social and behavioral context.} The feature representation models each post primarily through its textual content and basic metadata, but does not capture the interactive and relational dimensions of Reddit participation. Comment interactions, author reputation, subreddit-specific participation history, and ongoing community conversations all influence how posts are received, yet these signals are largely absent from the model. This became especially evident in the live experiment, where community members identified the posting account as suspicious based on behavioral patterns (high post-to-comment ratio, lack of engagement) rather than textual content alone.

\textbf{Temporal constraints.} The training data spans 2008–2022, but Reddit communities evolve continuously. Posting formats, moderation rules, and topical interests change over time, and models trained on historical data may learn patterns that are no longer valid. The dataset does not encode normative changes explicitly, limiting the model's ability to account for temporal drift between training and deployment periods.

\textbf{Minimal deployment sophistication.} The live experiment used a newly created account with no comment activity, no subreddit-specific participation history, and no attempt to mimic authentic user behavior beyond post content. A more sophisticated operator could incorporate aged accounts, realistic engagement patterns, and community-specific behavioral signals to reduce detection risk. The deployment results therefore represent a lower bound on what could be achieved with additional effort, though they also demonstrate that naive application of offline-validated models is insufficient for effective deployment.

\textbf{Distribution shift not fully diagnosed.} While the live experiment clearly demonstrated that offline performance does not transfer to deployment, the precise causes of the distribution shift remain incompletely understood. The negative correlation between predictions and outcomes suggests systematic miscalibration rather than random noise, but the thesis does not definitively identify whether this arises from spurious correlations in training data, differences in community response to unfamiliar accounts, systematic differences between historical and generated content, or other factors.

\section{Future Work}
\label{sec:future_work}

Several promising directions emerge from the findings and limitations of this thesis.

\textbf{Addressing distribution shift.} The most critical direction for future work is developing methods to close the gap between offline validation and deployment performance. This could involve training models on generated content with observed outcomes, incorporating domain adaptation techniques to account for differences between historical and generated posts, or developing features that explicitly capture differences in how communities respond to content from unfamiliar versus established accounts. Understanding and mitigating distribution shift is essential for any practical application of such systems.

\textbf{Incorporating behavioral and social context.} Future models could integrate richer signals beyond textual content and basic metadata. This includes author participation history, comment interaction patterns, recent subreddit activity, and temporal dynamics within communities. Such features may better capture the social context that influences post reception and could reduce the gap between isolated textual analysis and the full social process underlying community response.

\textbf{Subreddit-specific modeling.} Rather than applying a single embedding prompt and feature set across all communities, future work could adapt the encoding process to the explicit rules, norms, and stylistic expectations of individual subreddits. This might include subreddit-specific prompts for generating embeddings, community-specific feature engineering, or separate models trained for each target subreddit. Such specialization may improve the representation of community-specific fit and help distinguish between generally plausible posts and posts genuinely appropriate for particular communities.

\textbf{Broader subreddit coverage.} Expanding the analysis to a larger and more diverse set of subreddits would enable testing whether the observed patterns generalize across different topics, moderation regimes, and community structures. This would also make it possible to investigate whether certain types of communities are more or less susceptible to successful prediction and deployment, and whether the distribution shift observed in this thesis is consistent across different subreddit categories.

\textbf{Temporally adaptive modeling.} Since subreddit norms and moderation practices change over time, future work could investigate rolling training windows, temporally aware embeddings, or continual learning approaches designed to account for drift. This would address the limitation that models trained on historical data may learn outdated patterns that no longer apply in current community contexts.

\textbf{Behaviorally realistic deployment experiments.} The live experiment used minimal behavioral sophistication. Future work could examine the influence of account age, comment activity, posting rhythm, and subreddit-specific participation history on post reception. This would clarify to what extent deployment success depends on textual properties versus broader authenticity signals, and whether behavioral augmentation can overcome the prediction failures observed in this thesis.

\textbf{Alternative prediction targets and evaluation metrics.} While upvote ratio is a useful indicator of reception, future work could investigate alternative targets such as total score, comment count, removal probability, or downstream discussion quality. Multi-objective models that jointly predict multiple aspects of post performance may provide a more comprehensive understanding of community response and enable more flexible deployment strategies.

\textbf{Model interpretability and feature analysis.} A closer examination of which features drive prediction performance could reveal whether models rely primarily on topical relevance, stylistic similarity, emotional framing, or metadata-based shortcuts. This would improve understanding of what the models actually learn and help assess whether learned patterns reflect meaningful community preferences or artifacts of dataset composition and filtering.

\textbf{Defensive applications.} The techniques explored in this thesis could potentially be adapted for defensive purposes. Similar methods might be employed to detect strategically generated content, identify suspicious posting behavior, or flag accounts exhibiting patterns consistent with automated optimization. Investigating such safeguards would be an important step toward balancing methodological innovation with platform integrity concerns, particularly given the demonstration that content generation succeeds even when prediction fails.

\textbf{Cross-platform generalization.} Future work could examine whether the approaches and findings generalize to other online platforms beyond Reddit. Different platforms have different interaction mechanisms, moderation structures, and community norms, and testing the pipeline on platforms such as Twitter, Hacker News, or specialized forums would clarify how platform-specific the observed patterns and limitations are.

These directions collectively point toward both improving the technical effectiveness of such systems and better understanding their limitations, failure modes, and implications for platform integrity. The deployment failure documented in this thesis suggests that closing the gap between offline validation and real-world performance is a substantial challenge that requires more than incremental improvements to existing methods.