\chapter{Discussion}
\label{chap:discussion}

The results of this thesis demonstrate a sharp divergence between offline validation performance and live deployment outcomes. In controlled cross-validation experiments, semantic embeddings and structured metadata captured non-trivial signal related to post reception: the trained models achieved Spearman correlations exceeding 0.20 across multiple subreddits and explained a modest but meaningful portion of variance in upvote ratio. This indicates that historical Reddit data contains patterns related to community response that can be detected using publicly available features and off-the-shelf machine learning tools.

However, the live experiment revealed that offline predictive performance does not translate into effective real-world post selection. Model-approved posts scored approximately 7.4\% lower on upvote ratio than randomly selected posts, and predictions showed a strong negative correlation with actual outcomes ($\rho = -0.596$, $p < 0.0001$) within the model-approved subset. The model did not simply fail to improve upon random selection—it actively selected posts in the wrong order. This outcome demonstrates that the gap between historical prediction and deployment success is not merely a matter of degree, but reflects a fundamental distribution shift between training data and generated content. The models learned patterns from historical human-authored posts that did not generalize to newly created content from an unfamiliar account.

Critically, the random baseline treatment revealed that the content generation component of the pipeline produced viable posts: randomly selected generated content achieved a mean upvote ratio of 0.872, substantially exceeding both model-approved posts (0.808) and the historical training baseline (0.729). This indicates that the technical barrier to generating plausible community-appropriate content is lower than the barrier to accurately predicting which generated posts will succeed. The primary point of failure was not content generation, but model-guided selection.

A central limitation of the study lies in the composition of the dataset. Although the dataset is large in terms of total post count, the analysis covers only 19 subreddits. This is a very small subset compared to Reddit as a whole, and the selected communities are not necessarily representative of the broader platform. As a result, conclusions regarding cross-community generalizability, including the distinction between left-, right-, and neutral-labelled subreddit groups, should be interpreted cautiously. In particular, many of the subreddits categorized as neutral are discussion-oriented communities with their own strong posting norms and moderation practices. Differences observed between political leaning groups may therefore partly reflect differences in subreddit structure, expected post format, or moderation intensity rather than political orientation alone.

Another important limitation concerns data availability and selection bias. The final dataset was produced through multiple filtering stages. First, posts that could not be accessed or enriched through the Reddit API were removed, which reduced the Pushshift-based dataset by 23.38\%. Second, the minimum engagement constraint removed a further 35.3\% of the remaining posts. Relative to the initial dataset, only 50.2\% of posts were retained for modeling. These filtering steps improved the reliability of the target variable by excluding posts with missing metadata or extremely weak interaction. However, they also changed the composition of the dataset in systematic ways. The retained posts are more likely to reflect content that remained visible, complied with moderation rules, or received at least some degree of community attention. Consequently, the trained models do not represent all attempted participation on Reddit, but rather a filtered subset of posts that survived both archival and engagement thresholds.

This issue is likely even more severe than the retained dataset alone suggests. Posts that were removed immediately by moderators, blocked by automated filters, or never successfully appeared in a subreddit may not be represented in the archival data at all. This means that the dataset may systematically exclude certain forms of disallowed, low-quality, or suspicious content before any filtering by this study begins. As a result, the training data is biased toward observable and retained posts, which limits conclusions about the full distribution of content users or automated systems might attempt to submit.

A further limitation is that the prediction target itself is imperfect. Upvote ratio is a useful operationalization of post reception, but it is not a pure measure of quality, relevance, or persuasive success. It reflects a mixture of textual quality, topical fit, community agreement, early vote dynamics, ranking effects, and platform-specific mechanisms. A post may achieve a favorable upvote ratio not only because it is well written or well targeted, but also because it was posted at a favorable time, encountering a sympathetic early audience. The model might therefore learn patterns associated with observed community response, but these patterns should not be confused with a causal account of what makes a post intrinsically good or persuasive.

The pipeline is also limited in its representation of social context. Reddit posts are rarely interpreted in isolation. Comment interactions, author history, continuity across prior submissions, and ongoing community-specific conversations often shape how a post is perceived. The present approach models each post primarily through its textual content and associated metadata, but it does not capture the interactive and relational dimension of participation in online communities. This becomes especially relevant in the live experiment, where generated posts may appear suspicious or low-authenticity not because of their isolated wording, but because they lack the broader behavioral patterns associated with genuine users. Community members explicitly pointed to this issue in responses such as ``This user has 58 OPs and 1 comment. Please don't expect any engagement.'' or ``Why does op constantly post non sequitor one lines every day? Are they training an LLM or just a bot themselves.'' These reactions suggest that users do not evaluate posts only based on textual content, but also based on visible account behavior and participation patterns.

This also highlights a broader deployment limitation: strong offline performance does not automatically translate into real-world effectiveness. Historical prediction models are trained on human-authored posts embedded in natural community dynamics. In contrast, the live experiment introduces generated content selected by the model itself, thereby changing the data-generating process. This constitutes a form of distribution shift. The live experiment results demonstrate this shift concretely: models that achieved Spearman correlations exceeding 0.20 in cross-validation produced predictions with strong negative correlation ($\rho = -0.596$) when applied to generated content. This inversion cannot be explained by noise or reduced signal alone—it suggests systematic miscalibration. The model may have identified spurious correlations in the training set that appear predictive in historical data but fail or reverse when applied to newly created content. Alternatively, moderators and users may respond differently to content from an unfamiliar account compared to established community members, introducing dynamics not captured during training on historical posts from authentic users. The live experiment therefore provides an important counterbalance to the offline results by showing that model-guided selection can actively harm performance relative to random baseline, even when the underlying content generation produces viable posts.

Temporal instability presents an additional limitation. Reddit communities evolve over time, and both user expectations and moderation rules may change substantially. Posting formats that were previously common and successful may later become discouraged, redirected into megathreads, or removed altogether. For example, a subreddit may historically reward a certain type of recommendation request while later deciding that such posts should only appear in designated discussion threads. Since the training data does not always encode these normative changes explicitly, models trained on historical data may partially learn outdated signals. This reduces the long-term stability of the approach and complicates deployment in changing online environments.

\section{Platform Integrity Implications}

The findings of this thesis have implications for online platform integrity and content moderation, though the implications are more nuanced than the feasibility framing alone suggests. The live experiment demonstrated both that an end-to-end pipeline can be constructed with minimal resources and that model-guided post selection failed catastrophically in deployment. These two findings must be interpreted together.

\subsection{Demonstrated Capabilities and Limitations}

The pipeline demonstrated several capabilities that remain relevant to platform integrity concerns:

\textbf{Low barrier to entry.} The pipeline was constructed using only publicly available data, off-the-shelf tools, and modest computational resources. Data collection, model training, content generation, and automated posting were all operational without specialized infrastructure. This demonstrates that the technical barrier to building such systems is low, even if deployment effectiveness remains uncertain.

\textbf{Viable content generation.} The random baseline treatment revealed that generated content can achieve favorable reception: randomly selected posts achieved a mean upvote ratio of 0.872, exceeding the historical training baseline of 0.729. This indicates that language models can produce posts that communities do not systematically reject, even when those posts come from unfamiliar accounts. The generation component succeeded where the prediction component failed.

\textbf{Evading content-based detection.} Generated posts were topically relevant, grammatically correct, and stylistically similar to organic community discussions. Moderators and community members occasionally identified the account as suspicious based on posting patterns and lack of comment engagement, but the content itself was not flagged as spam or off-topic in most cases. This suggests that content-based detection systems designed to identify low-quality or irrelevant submissions may not reliably detect model-generated posts optimized for community fit.

However, the live experiment also revealed critical limitations:

\textbf{Model-guided selection failed.} Predictions not only failed to improve upon random selection, but actively selected posts in the wrong order. This demonstrates that offline validation performance does not guarantee deployment effectiveness. A malicious actor using a similar approach might achieve no better results than random posting unless they address the distribution shift between historical training data and generated content.

\textbf{Moderation resistance.} Four of nine targeted subreddits banned the posting account, and an additional 17 posts were individually removed. These moderation responses suggest that automated posting faces social and procedural barriers beyond content quality alone. Community members explicitly identified the account as suspicious based on posting patterns, lack of engagement, and behavioral signals that the model could not optimize.

\subsection{Revised Threat Model}

Given these findings, the threat landscape is more complex than a simple feasibility demonstration would suggest. Several scenarios remain concerning despite the deployment failure:

\textbf{Adversarial adaptation and iteration.} The present study did not implement adaptive feedback loops or iterative retraining. A malicious actor could observe deployment outcomes, identify distribution shift issues, and refine the pipeline accordingly. This might include retraining models on generated content that performed well, adjusting generation prompts based on community response, or incorporating behavioral features that were absent in the initial design. The failure documented here does not prove that such systems cannot be made effective—it demonstrates that naive deployment of offline-validated models is insufficient.

\textbf{Random generation as a baseline threat.} The random baseline treatment achieved strong performance on upvote ratio, indicating that even unoptimized generated content can be well-received. An actor who generates large volumes of plausible content and posts randomly may achieve favorable reception without requiring accurate prediction. This lowers the technical sophistication required for certain influence objectives, particularly those focused on visibility rather than precision targeting.

\textbf{Behavioral augmentation.} The live experiment used a minimal posting setup: a newly created account with no comment activity, no subreddit-specific participation history, and no attempt to mimic authentic user behavior beyond the post content itself. A more sophisticated operator could incorporate aged accounts, realistic comment patterns, varied posting rhythms, and community-specific engagement to reduce detection risk. These augmentations would not address the prediction failure directly, but could improve overall operational viability.

\textbf{Coordinated low-precision operations.} Even if individual posts are not optimally selected, coordinated posting across multiple accounts and subreddits could achieve narrative amplification objectives. The goal of such operations may not be to maximize engagement on each post, but to create the appearance of distributed organic discussion on a chosen topic. In this scenario, prediction accuracy is less critical than content plausibility and posting volume.

\subsection{Detection Opportunities}

The deployment failure and moderation resistance observed in this thesis also suggest several detection opportunities:

\textbf{Behavioral pattern analysis.} Community members identified the posting account as suspicious based on observable behavior: high post-to-comment ratio, lack of engagement, and repetitive posting patterns. Platforms could develop signals based on these patterns to flag accounts for review, even when individual posts appear legitimate.

\textbf{Account history and credibility signals.} The account used in this experiment was newly created and lacked established participation history. Platforms could impose stricter requirements on new accounts, require demonstrated engagement before allowing posts, or weight content from established users more heavily in ranking algorithms.

\textbf{Community-driven moderation.} Several subreddits successfully identified and banned the posting account based on moderator judgment and community reports. Empowering moderators with better tools and signals may improve detection, though this approach does not scale uniformly across all communities and places significant burden on volunteer moderators.

\textbf{Karma and participation requirements.} Some targeted subreddits could not be posted to at all due to minimum karma thresholds that the newly created account did not meet. These requirements present an effective barrier against low-effort spam and newly created bot accounts. However, such barriers are not insurmountable: a more resourceful operator could circumvent karma requirements by purchasing established accounts, gradually building karma through strategic participation in high-traffic subreddits, or using language models to generate plausible comments on popular posts. While these tactics require additional effort and sophistication, they remain within the technical capabilities demonstrated in this thesis. Karma requirements therefore function as a friction mechanism rather than an absolute barrier, raising the operational cost of automated posting without preventing it entirely.

\subsection{Responsible Disclosure Considerations}

This thesis presents a methodological demonstration rather than a deployed attack system. The decision to publish these methods, including the deployment failure, rests on several considerations:

First, the techniques used are not novel individually. Scraped Reddit data, transformer embeddings, gradient boosting, and generative language models are all established technologies. The contribution is demonstrating that they can be combined into a functional pipeline and documenting both the capabilities and limitations of such systems in real deployment.

Second, transparency about both platform vulnerabilities and the limitations of adversarial techniques is essential for informed policy and technical responses. Documenting that model-guided selection failed catastrophically is as important as documenting that content generation succeeded. This enables platform operators, researchers, and policymakers to assess risks accurately rather than overestimating the immediate threat posed by such systems.

Third, the experimental deployment was designed to minimize harm. The posting volume was low, the content was constrained to avoid trending topics or coordinated messaging, and no adaptive optimization was performed. The objective was validation of feasibility and measurement of actual deployment outcomes, not demonstration of maximum impact.

The position taken in this thesis is that the benefits of open research and public awareness—including documentation of failure modes—outweigh the risks of marginal increases in adversarial capability. The deployment failure does not eliminate platform integrity concerns, but it demonstrates that the gap between offline validation and real-world effectiveness is substantial and should not be underestimated.

\section{Summary}

Taken together, these findings paint a complex picture of predictability and deployment effectiveness in Reddit post optimization. Offline experiments demonstrated that semantic and structured features capture meaningful signal related to post reception, achieving moderate predictive accuracy in cross-validation. However, the live experiment revealed that this offline performance does not translate to effective real-world post selection. Model-guided selection not only failed to outperform random baseline, but actively selected posts in the wrong order, while randomly selected generated content achieved favorable reception. This divergence points to a fundamental distribution shift between historical training data and generated content deployed from an unfamiliar account. The observed limitations—including dataset composition constraints, selection bias, imperfect prediction targets, missing social context, temporal instability, and systematic deployment failure—indicate that post success cannot be reliably engineered from textual features and historical patterns alone. At the same time, the demonstration that viable content can be generated and that the technical barrier to pipeline construction is low suggests ongoing relevance for platform integrity research. The limitations identified in this chapter point to several promising directions for future work, including the incorporation of richer behavioral signals, broader subreddit coverage, temporally adaptive modeling strategies, and methods for addressing distribution shift between training and deployment contexts.