\chapter{Future Work}
\label{chap:future_work}

Several promising directions emerge from the limitations and findings of this thesis.

First, future work could explore subreddit-specific encoder prompts. Rather than applying a single embedding prompt across all communities, the encoding process could be adapted to the explicit rules, norms, and stylistic expectations of individual subreddits. For example, embeddings could be generated with prompts that emphasize how well a post aligns with the rules and conventions of a given community. This may improve the representation of community-specific fit and help distinguish between generally plausible posts and posts that are genuinely appropriate for a particular subreddit.

Second, the generation pipeline could be improved through more context-sensitive prompting. Instead of relying on static prompts, future systems could incorporate information about currently salient topics, recent discussions, or ongoing trends within a target subreddit. This may lead to generated posts that are not only linguistically coherent, but also more timely and topically relevant to the community in which they are posted.

A further important direction is the incorporation of richer social context. Reddit posts are typically not evaluated in isolation, but in relation to comment interactions, user behavior, and broader community dynamics. Future models could therefore integrate comment threads, author participation history, or signals derived from recent subreddit activity. Such additions may improve predictive performance while also producing a more realistic representation of how post reception emerges in practice.

Future studies should also evaluate the approach on a broader and more diverse set of subreddits. The present work is limited to 19 communities, which constrains the generalizability of the findings. Expanding the analysis to a larger number of subreddits would make it possible to test whether the observed patterns persist across different topics, moderation regimes, and community structures.

Another promising avenue is temporally adaptive modeling. Since subreddit norms, moderation rules, and topical interests change over time, models trained on historical data may become less effective in later settings. Future work could investigate rolling training windows, temporally aware embeddings, or other approaches designed to account for such drift.

The live posting component could likewise be extended through more behaviorally realistic experiments. In particular, future work could examine the influence of account age, comment activity, posting rhythm, and subreddit-specific participation history on post reception. This would help clarify to what extent success depends on textual properties alone and to what extent it relies on broader signals of authenticity.

In addition, future work could investigate alternative target variables beyond upvote ratio. While upvote ratio is a useful indicator of reception, it captures only one dimension of community response. Other measures, such as total score, number of comments, removal probability, or downstream discussion quality, may provide a more comprehensive understanding of post performance.

Another valuable extension concerns model interpretability. A closer analysis of which features drive prediction performance could reveal whether the models rely primarily on topical relevance, stylistic similarity, emotional framing, or metadata-based shortcuts. This would improve the interpretability of the results and help assess whether the learned patterns reflect meaningful community preferences or artifacts of the dataset.

Finally, future work should also consider defensive applications. Since the methods explored in this thesis could potentially be misused to optimize manipulative or low-authenticity participation, similar techniques might also be employed to detect strategically generated content or identify suspicious posting behavior. Investigating such safeguards would be an important step toward balancing methodological innovation with platform integrity concerns.