\chapter{Related Work}
\label{chap:relatedwork}

Research relevant to this thesis spans several related areas: the prediction of online content popularity, the prediction of controversy and other forms of community reaction, the optimization or generation of engagement-oriented content, and the study of influence operations on social platforms. While these literatures provide important building blocks, they rarely address whether a lightweight pipeline built entirely from public platform data and off-the-shelf tools can be used to generate and selectively deploy posts that are more likely to be positively received by a target community. This thesis addresses that gap.

\section{Prediction of Popularity and Community Reception}

A substantial body of prior work has examined whether the eventual success of online content can be predicted from features available at or shortly after publication. In Reddit-specific work, Segall et al.~\cite{segall2012predicting} used features such as author identity, submission time, and textual properties to predict post popularity. Their work established an important baseline assumption for later research: community response on Reddit is not entirely random, but can be modeled from observable characteristics of posts and authors.

Other work has relied more heavily on post-publication interaction signals. Terentiev et al.~\cite{terentiev2014predicting} predicted post popularity using characteristics of the first ten comments, while Wigsnes et al.~\cite{wigsnes2019predicting} used statistics observed one hour after publication. These studies demonstrate that early engagement contains substantial predictive information. However, such approaches are less suitable for settings in which a decision must be made before or at the moment of posting. A system intended to generate candidate posts and filter them prior to publication cannot rely on reactions that only emerge after submission. These approaches are therefore valuable for retrospective prediction, but less relevant for pre-publication selection.

Related work has also extended prediction beyond submissions to the level of discussion contributions. Deaton et al.~\cite{deaton2017using} examined the prediction of comment popularity, showing that community evaluation can also be modeled at the level of individual contributions within a thread. This reinforces the broader point that platform-native response signals are computationally tractable, although the present thesis focuses specifically on submission-level reception.

A further distinction concerns the operationalization of the target variable. Much prior work defines popularity in terms of attention or engagement volume, such as total score, number of comments, or overall visibility. In contrast, this thesis focuses on upvote ratio as a proxy for community approval. This distinction is important. Measures such as score or comment count are strongly affected by exposure, timing, and platform dynamics~\cite{chan2025examining, chan2024understanding, barnes2024topicality}, whereas upvote ratio can be understood as a closer approximation of how positively users responded once they encountered the content. The present work is therefore less concerned with maximizing visibility in a generic sense than with estimating whether a post is likely to be received favorably within a specific subreddit.

Stoddard~\cite{stoddard2015popularity} approached this issue from a complementary perspective by analyzing the relationship between observed popularity and intrinsic quality on Reddit and Hacker News. Using time-series voting data and a model intended to control for position and visibility effects, Stoddard argued that voting systems often surface content with substantial underlying quality. This work is important for understanding how popularity emerges on social platforms, but it remains retrospective in orientation: quality is inferred from observed post-publication behavior rather than predicted before submission. By contrast, the present thesis is concerned with pre-publication estimation of likely community approval using only publicly obtainable information.

\section{Prediction of Controversy and Other Community Outcomes}

Popularity or approval is not the only community outcome studied in prior work. Hessel and Lee~\cite{hessel2019something} investigated the early prediction of controversial Reddit posts, defining controversy through mixed positive and negative community response. Using features derived from early comment trees, they showed that textual and structural interaction signals improve predictive performance compared to post-time features alone. Particularly relevant for the present thesis is their finding that controversy prediction is not equivalent to popularity prediction: models trained for one outcome do not transfer well to the other.

This distinction is important because it illustrates that predictive systems must be aligned with their actual downstream objective. A model optimized to identify divisive content is not necessarily useful for identifying content that will be positively received. The present thesis therefore treats community approval as a distinct prediction target rather than assuming it can be inferred from broader engagement or disagreement-related measures.

\section{From Predicting Reception to Optimizing Content}

Most prior work in this area stops at prediction. A separate line of research asks how content can be actively optimized to attract more attention or engagement. One closely related area is clickbait research. Potthast et al.~\cite{potthast2016clickbait} focus on the detection of clickbait headlines, while other work has examined the generation of clickbait-style text or the use of synthetic clickbait for classification-related purposes~\cite{xu2019clickbait,shu2018deep}. This literature demonstrates that textual framing can be manipulated systematically in order to influence audience behavior.

However, clickbait-oriented work differs from the present thesis in two important respects. First, it typically focuses on headlines in publisher-driven contexts rather than full posts embedded in community-specific interaction spaces. Second, it generally treats success in terms of clicks or attention rather than positive reception by a specific audience with its own norms, expectations, and moderation practices.

Recent work using large language models extends this optimization logic further. Zhao et al.~\cite{zhao2025amplifying}, for example, investigate the use of LLMs for personalized influential content generation intended to increase engagement and diffusion on social media. This line of research is closely related to the present thesis because it demonstrates that generative systems can be explicitly oriented toward downstream social impact metrics. However, the present work differs in both framing and evaluation target. Rather than personalizing content to maximize spread, this thesis examines whether subreddit-specific approval can be modeled from historical public data and then used to score and rank LLM-generated candidate posts prior to submission.

This distinction between generation alone and generation combined with predictive filtering is central. A language model can produce many plausible candidate posts, but without an external scoring mechanism it has no grounded estimate of which outputs are more likely to align with a particular community's preferences. The contribution of this thesis therefore lies not merely in using an LLM to generate Reddit-style text, but in combining generation with a predictive model trained on historical community response. This yields a simple but operationally meaningful pipeline: generate multiple candidate posts, estimate their likely approval, and select only the most promising outputs for publication.

\section{Influence Operations and Low-Barrier Manipulation}
\label{sec:influence_ops}

A broader literature has examined organized manipulation, propaganda, trolling, and disinformation campaigns on online platforms. Understanding these real-world precedents is essential for contextualizing the potential misuse of the methods developed in this thesis.

\paragraph{Documented Influence Campaigns}

Large-scale influence operations have repeatedly demonstrated the vulnerability of social media platforms to coordinated manipulation. The 2016 U.S. presidential election saw extensive interference by Russian-linked actors operating through the Internet Research Agency (IRA), which deployed thousands of inauthentic accounts to amplify divisive content and suppress voter turnout~\cite{badawy2018analyzing,zannettou2019disinformation}. Similar operations have been documented in the context of Brexit~\cite{bastos2019brexit}, the 2017 French elections~\cite{DBLP:journals/corr/Ferrara17aa}, and numerous other political events worldwide~\cite{woolley2018computational}.

These campaigns share several common characteristics: they exploit platform affordances such as recommendation algorithms and trending mechanisms; they adapt content to target-specific communities and ideological groups; and they operate at scale through a combination of human coordination and automated tooling. Importantly, detection efforts have consistently lagged behind deployment, with many operations discovered only after elections or referendums had concluded~\cite{shao2018spread}.

\paragraph{Troll Farms and Coordinated Inauthentic Behavior}

Linvill and Warren~\cite{linvill2020troll} provide a detailed behavioral analysis of IRA-linked troll accounts, identifying distinct operational roles including right-leaning, left-leaning, and hashtag-gaming personas. Their work demonstrates that successful influence operations do not rely solely on technical sophistication but on understanding and mimicking the linguistic patterns, posting schedules, and engagement strategies typical of authentic users within target communities.

This behavioral mimicry is precisely what predictive models trained on historical community data enable at scale. Where human operatives must learn community norms through observation and trial-and-error, a regression model trained on millions of historical posts can encode those norms as statistical patterns and apply them to newly generated content.

\paragraph{Automation and Scalability}

The technical barriers to deploying influence operations have decreased substantially. Early bot networks were detectable through crude heuristics such as posting frequency, account age, and lexical repetition~\cite{varol2017online}. Modern detection methods have grown more sophisticated, incorporating graph-based coordination analysis~\cite{cresci2017paradigm}, temporal behavioral patterns~\cite{yang2020scalable}, and linguistic anomaly detection~\cite{hayawi2022anti}.

However, as detection methods improve, so too do evasion techniques. Advances in natural language generation---particularly large language models capable of producing contextually appropriate, stylistically diverse text---have made it increasingly difficult to distinguish automated content from human-authored posts based on linguistic features alone~\cite{zellers2019defending, solaiman2019release}.

The present thesis contributes to this trajectory by demonstrating that community-specific optimization can be achieved through regression models trained on public data. Unlike earlier bot detection research, which assumed that inauthentic content would exhibit detectable anomalies, this work shows that models can be explicitly trained to produce content that aligns with community-specific approval patterns.

\paragraph{Low-Barrier Tools and Democratized Manipulation}

A particularly concerning trend is the commodification and democratization of influence tools. Commercial services offering fake engagement, coordinated upvoting, and persona management are widely available~\cite{thomas2013trafficking}. Open-source toolkits for automated posting, account management, and content scheduling reduce the technical expertise required to operate at scale.

The pipeline demonstrated in this thesis fits within this broader ecosystem. It requires no privileged platform access, no proprietary datasets, and no specialized infrastructure beyond what is available through academic computing resources or cloud services. Embedding generation and model training can be performed on modest GPU hardware, and the computational requirements are well within the reach of individual researchers or small groups. The Pushshift archive is publicly accessible. The Reddit API is available to any registered user. Transformer-based embedding models and XGBoost are standard open-source tools. Large language models capable of generating plausible discussion posts are freely available through commercial APIs or can be run locally.

This accessibility is a double-edged outcome. On one hand, it enables academic research, platform auditing, and transparency efforts. On the other hand, it lowers the barrier to entry for malicious actors, enabling influence operations by non-state actors, commercial entities, and ideologically motivated individuals who previously lacked the resources or expertise to deploy such systems.

\paragraph{Platform Responses and Detection Challenges}

Social media platforms have implemented various countermeasures, including 
rate limiting, CAPTCHA challenges, phone verification, account age 
requirements, and behavioral anomaly detection~\cite{jhaver2019does}.

More fundamentally, platforms face a detection dilemma: content that is optimized for community approval is, by definition, difficult to distinguish from genuinely popular content. A post that successfully mimics the linguistic patterns, topical framing, and stylistic conventions of a target community will pass most content-based filters. The primary remaining signal is behavioral---unusual posting patterns, coordination across accounts, or rapid scaling---but these signals can be obscured through careful operational design.

The present work does not solve these detection challenges. Rather, it highlights the growing feasibility of generating community-tailored content at scale, a capability that complicates platform moderation and trust-and-safety efforts.

\section{Positioning of the Present Thesis}

Taken together, prior work establishes that online reactions can be modeled, that early interaction signals often improve prediction, that textual framing can be optimized for engagement, and that social platforms are vulnerable to strategic manipulation. However, an important gap remains between these literatures.

First, much research on content success focuses on attention or engagement volume rather than community approval. This thesis instead models upvote ratio as a proxy for how positively a subreddit receives a post. Second, many strong predictive approaches depend on post-publication signals such as early comments or early voting patterns, whereas the present work is explicitly concerned with pre-publication selection. Third, while recent LLM-based work investigates engagement-oriented content generation, less attention has been given to lightweight generation-and-filtering pipelines grounded in historical public community data.

This thesis contributes to that gap in three ways. It evaluates which publicly observable features are useful for predicting subreddit-specific approval; it extends that predictive setup into a pipeline in which LLM-generated candidate posts are ranked and filtered by a trained model; and it evaluates the operational feasibility of this approach through a live experiment involving real submissions.

The live experiment is not intended to demonstrate broad real-world influence capability, but to test whether the generation-and-selection pipeline functions outside of an offline evaluation setting. The contribution of the thesis is therefore not simply another predictor of Reddit post success. Rather, it demonstrates that community-tailored content optimization can be implemented with modest means using public data and off-the-shelf tools. Precisely because the technical barrier is low, this feasibility should be understood as a warning signal.