\chapter{Subreddit Rules and Guidelines}
\label{app:subreddit_rules}

This appendix documents the community rules and guidelines for each subreddit included in the popularity prediction and live Reddit posting experiment. All information was retrieved via the Reddit API in February 2025. Subreddits are listed alphabetically, with subscriber counts, creation dates, and complete rule sets as enforced at the time of the experiment.

\subsection{anarchism}
\textbf{Subscribers:} 188,027 \\
\textbf{Created:} January 2008 \\
\textbf{Description:} Anarchism is a social movement that seeks liberation from oppressive systems of control including but not limited to the state, capitalism, racism, sexism, ableism, speciesism, and religion. Anarchists advocate a self-managed, classless, stateless society without borders, bosses, or rulers where everyone takes collective responsibility for the health and prosperity of themselves and the environment.

\textbf{Account Status:} Banned during experiment.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{AOP (Anarchist Online Policy):} This is an anarchist space, anti-capitalists of all stripes are welcome but fundamental challenges to anarchist theory are not. Debate and the exchange of ideas is encouraged but arguments which are sexist, racist, homophobic, transphobic, ableist, or which otherwise exhibit oppressive or antagonistic attitudes will not be tolerated.
    
    \item \textbf{Egregious Bigotry:} No racism, sexism, ableism, homophobia, transphobia, or similar forms of bigotry. No nationalist, authoritarian-apologia, or apologia for oppression.
    
    \item \textbf{Bad Faith Antipathy:} No antagonism, trolling, flaming, or any similar displays of bad faith engagement with the community.
    
    \item \textbf{Off-topic Content:} Stay on topic. Posts should be relevant to anarchism or the anarchist movement.
    
    \item \textbf{Spam:} Spam will be removed. This includes promotional material, referral/affiliate links, or material that is clearly off-topic or inappropriate for the subreddit.
    
    \item \textbf{Sectarianism:} Constructive discussion of goals, tactics, ideology, and philosophy is encouraged, but posts that devolve into partisan name-calling or other forms of sectarianism will be removed.
    
    \item \textbf{Image/Video Posts:} Image or video posts should be accompanied by a text post, or at bare minimum should be started off by a top level comment from OP. If after 15 minutes there isn't a clarifying comment, the post will be removed.
    
    \item \textbf{Meta Content:} Meta posts about r/anarchism belong in r/metanarchism. This includes posts about moderation, community direction, sub rules, drama in other subs, etc.
    
    \item \textbf{Support for Hierarchy:} No support for oppressive hierarchies such as capitalism, the state, white supremacy, patriarchy, etc.
\end{enumerate}

\subsection{changemyview}
\textbf{Subscribers:} 3,095,798 \\
\textbf{Created:} January 2013 \\
\textbf{Description:} A place to post an opinion you accept may be flawed, in an effort to understand other perspectives on the issue. Enter with a mindset for conversation, not debate.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{Explain the reasoning behind your view:} You must personally hold the view and demonstrate that you are open to it changing. Demonstrate that you're willing to engage with the discussion.
    
    \item \textbf{You must reply to comments from others within 3 hours:} OP must reply to comments within 3 hours to maintain their post.
    
    \item \textbf{Don't be rude or hostile to others:} All users must demonstrate a willingness to participate in an environment of mutual respect. Don't be rude or hostile to other users.
    
    \item \textbf{Award a delta if you've acknowledged a change in your view:} If you have acknowledged/hinted that your view has changed in some way, please award a delta.
    
    \item \textbf{Only post if you are willing to have a conversation:} You must be willing to have your perspective challenged and to challenge others. Posts intended solely to express a perspective, rant, or soapbox are not appropriate.
    
    \item \textbf{No low effort posts:} Your post must contain sufficient detail and context. Questions should seek to understand existing perspectives, not to create a referendum on a topic.
    
    \item \textbf{Fresh Topic Friday:} On Fridays, only Fresh Topics are permitted. Posts on common topics may be removed at moderator discretion.
\end{enumerate}

\subsection{Coffee}
\textbf{Subscribers:} 609,844 \\
\textbf{Created:} January 2008 \\
\textbf{Description:} r/Coffee is a place to discuss any and all things coffee. From roasting, to brewing, to reviewing - it's all here!

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{General Tone:} Be respectful, kind, empathetic, and nice. If a user is mean spirited or rude, report them and move on. Do not engage or escalate. Discussion should not devolve into fights where people are being called names or dealing with insults and vitriol. Keep it kind.
    
    \item \textbf{No Purchase Advice:} All ``help me buy'' questions should go in the Daily Question Thread or r/espresso. Purchase advice questions include ``What grinder should I buy?'', ``What beans are good?'', ``Where can I buy X?'', ``Is X worth the money?'', etc.
    
    \item \textbf{Brew Help Requests:} Troubleshooting and brew help requests belong in the Daily Question Thread. Topics requiring quick answers or minimal discussion belong in the Daily thread to keep the sub focused on discussion-oriented posts.
    
    \item \textbf{No Low-Effort Posts:} Posts lacking in substance or requiring minimal engagement will be removed. Examples include polls, simple yes/no questions, posts that can be answered by searching, memes, or off-topic tangentially coffee-related posts.
    
    \item \textbf{Recipes, Images, and Videos:} Recipe, image, and video posts require explanatory top-level comment by OP. If no context is provided within 15 minutes, the post will be removed. Posts showing coffee or equipment must include details about what you're sharing and why.
    
    \item \textbf{No Unconstructive Posts:} Rants, unconstructive complaints, or posts that solely exist to criticize others or their choices are not welcome.
    
    \item \textbf{Elitist Nonsense:} Coffee needs to walk a fine line here; our line is ``education'' - is the content presented without personal judgement and with teaching that is useful. We have a very low tolerance for perspectives that want to gatekeep coffee or engage in elitist circlejerking.
    
    \item \textbf{Promotion:} Do not promote businesses, projects, or causes that you have ties to under any circumstances. This includes owners, investors, employees, family members, or good friends.
    
    \item \textbf{Shilling / Sockpuppetry:} Misrepresenting affiliations or lying about connections to products, businesses, or content is strictly prohibited. Be honest about your entanglements.
    
    \item \textbf{Affiliates \& Referrals:} Affiliate and referral links are not welcome, including sites or content containing affiliates, even if the person posting is not tied to the site in question.
    
    \item \textbf{Product Release \& Pre-Release Hype:} Product reviews belong in Battlestation threads. Nothing about unreleased or recently-released products is permitted until real users have had time to provide honest reviews.
    
    \item \textbf{No Crowdfunding Projects:} Absolutely no crowdfunding projects in any stage. Once a crowdfunding project becomes a normal retail product that people own, moderators will determine when to relax this rule.
    
    \item \textbf{No Surveys / Market Research:} No surveys, polls, market research, or ``what should I make'' posts are permitted.
    
    \item \textbf{Medical Advice:} Coffee-related health advice or health-science articles are not appropriate. Community members are not medical professionals. Consult a physician for health concerns related to coffee consumption.
    
    \item \textbf{Mod Discretion:} Moderators reserve the right to remove content and issue bans as needed for the health of the community.
\end{enumerate}

\subsection{Conservative}
\textbf{Subscribers:} 1,348,594 \\
\textbf{Created:} January 2008 \\
\textbf{Description:} We provide a place on Reddit for conservatives, both fiscal and social, to read and discuss political and cultural issues from a distinctly conservative point of view.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{Civility:} Be civil, follow any flair guidelines.
    
    \item \textbf{Racism:} No racism.
    
    \item \textbf{Spam:} Don't spam article submissions (this doesn't apply to comments). Limit 4 per hour.
    
    \item \textbf{Brigading:} No vote brigading.
    
    \item \textbf{Shitpost:} Shit posts will be removed at moderator discretion and the user may be banned.
    
    \item \textbf{Title not from article:} Submission headlines must match the article headline or quote the article.
    
    \item \textbf{Violates Mission Statement:} Do not violate the Mission Statement (We provide a place on Reddit for conservatives, both fiscal and social, to read and discuss political and cultural issues from a distinctly conservative point of view).
\end{enumerate}

\subsection{DebateReligion}
\textbf{Subscribers:} 197,518 \\
\textbf{Created:} June 2011 \\
\textbf{Description:} A place to discuss and debate religion.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{Meta posts:} Meta posts and moderation complaints are to be directed to the General Discussion thread or sent directly to the moderators.
    
    \item \textbf{Fresh Topic Friday:} On Fridays, posts must be on a topic that has not been discussed on this subreddit within the past two months.
    
    \item \textbf{Be Respectful:} Personal attacks, slurs, bigotry, etc. are not permitted and may result in a ban.
    
    \item \textbf{No Low Effort:} All posts and comments should contribute to discussion. One sentence posts, posts with no argument, or low quality comments may be removed.
    
    \item \textbf{Thesis Statement and Argument:} All posts must contain a thesis statement and an argument supporting that thesis. Posts without clear arguments may be removed.
    
    \item \textbf{Quality Rule:} Posts must meet minimum quality standards including proper formatting, clear argumentation, and substantive engagement with the topic.
    
    \item \textbf{Civilization:} Be appropriately respectful in tone. Avoid being hostile, belligerent, or combative.
    
    \item \textbf{Substantial Top-Level Comments:} All top-level comments must seek to refute the post through substantial engagement with its core argument.
    
    \item \textbf{Participate in Good Faith:} Do not misrepresent or mischaracterize positions. Engage honestly and charitably.
    
    \item \textbf{Don't Preach:} Posts should advance arguments rather than merely proclaim beliefs. Proselytizing is not permitted.
\end{enumerate}

\subsection{DecidingToBeBetter}
\textbf{Subscribers:} 911,382 \\
\textbf{Created:} November 2011 \\
\textbf{Description:} A force for self-improvement, goodness, and togetherness that helps humanity eliminate evil. Progression is key, so if you have decided to leave the bad behind, this is the place for you.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{Deciding to be Better:} All content must be related to the process of self-improvement and deciding to be a better person.
    
    \item \textbf{Be Civil:} Engage respectfully. Harassment, hate speech, personal attacks, and other uncivil behavior will result in removal and/or bans.
    
    \item \textbf{No Advertisements or Surveys:} No advertisements, market research, surveys, donation requests, affiliate links, or petitions.
    
    \item \textbf{Give Support:} Posts should be focused on giving or receiving constructive support. Rants without substance or low-effort posts may be removed.
    
    \item \textbf{Mental Health Crises:} We are not mental health professionals. Posts about suicide, self-harm, or mental health emergencies should be directed to appropriate crisis resources.
\end{enumerate}

\subsection{democrats}
\textbf{Subscribers:} 177,043 \\
\textbf{Created:} January 2008 \\
\textbf{Description:} The Democratic Party is fighting for a country where everyone, no matter who they are, where they come from, or who they love, can reach their full potential and live with dignity and respect.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{Keep it civil:} Do not personally insult other Redditors, or post discriminatory content.
    
    \item \textbf{Be a Democrat:} This is a subreddit for Democrats. Republicans and Independents are welcome, but please keep your posts substantive and clearly relevant.
    
    \item \textbf{No spam:} Links to outside organizations or fundraising pages must be relevant to the Democratic Party.
    
    \item \textbf{Be substantive:} Low-effort posts, memes, and image macros are subject to removal at moderator discretion.
    
    \item \textbf{No conspiracy theories:} Do not promote conspiracy theories.
\end{enumerate}

\subsection{Fantasy}
\textbf{Subscribers:} 1,773,104 \\
\textbf{Created:} January 2008 \\
\textbf{Description:} r/Fantasy is the internet's largest discussion forum for the greater Speculative Fiction genre. We welcome respectful dialogue related to speculative fiction in literature, games, film, and the wider world.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{Be Kind:} Engage in good-faith discussion. Respect differences in opinion. Harassment, insults, and trolling are not tolerated.
    
    \item \textbf{Self-Promotion Policy:} Self-promotion is allowed within strict limits. Authors may self-promote once per month in specific threads. Review the full policy before posting.
    
    \item \textbf{Low-Effort Posts:} Posts must generate meaningful discussion. Simple questions, yes/no polls, and low-effort content should go in the Daily Recommendation Requests and Simple Questions thread.
    
    \item \textbf{Off-Topic Posts:} Posts must be related to speculative fiction or topics of broad interest to the r/Fantasy community.
    
    \item \textbf{No Piracy:} Do not link to or request pirated content.
    
    \item \textbf{No AI-Generated Content:} AI-generated text, cover art, or other content is not permitted.
    
    \item \textbf{Hide Spoilers:} Use spoiler tags appropriately. Be considerate of others' reading experiences.
    
    \item \textbf{Review Policy:} Reviews must follow community guidelines. Focus on the work, not personal attacks on the author.
    
    \item \textbf{No Surveys:} Surveys, polls, and market research require moderator approval.
\end{enumerate}

\subsection{Frugal}
\textbf{Subscribers:} 3,279,298 \\
\textbf{Created:} January 2008 \\
\textbf{Description:} Frugality is the mental approach we each take when considering our resource allocations. It includes time, money, convenience, and many other factors.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{Relevance:} All posts must be directly related to frugality.
    
    \item \textbf{Self-Promotion:} Self-promotion, advertising, solicitation, surveys, coupon trading, selling, referral links, and other forms of marketing are not permitted.
    
    \item \textbf{Civility:} Be civil and respectful in all interactions.
    
    \item \textbf{Politics:} Posts should avoid partisan political discussion and focus on frugality.
    
    \item \textbf{Quality:} Low-effort posts, reposts, and commonly asked questions may be removed.
\end{enumerate}

\subsection{geopolitics}
\textbf{Subscribers:} 1,438,421 \\
\textbf{Created:} September 2008 \\
\textbf{Description:} Serious discussion of international relations and geopolitics.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{Follow the Rules:} Read and follow all community rules and Reddit's Content Policy.
    
    \item \textbf{Quality Comments:} Comments should be substantive and contribute to discussion. Low-effort comments will be removed.
    
    \item \textbf{Quality Submissions:} Submissions must meet quality standards. Include a submission statement explaining the article's relevance to geopolitics.
    
    \item \textbf{Submission Statement:} All link posts require a submission statement of at least 150 characters posted within 30 minutes.
    
    \item \textbf{Maintain Civility:} Be respectful and civil in all interactions.
    
    \item \textbf{No Low-Quality Comments:} Avoid one-liners, jokes, memes, or other low-quality content in top-level comments.
    
    \item \textbf{No Editorialized Titles:} Use the original article title or provide an accurate, neutral description.
\end{enumerate}

\subsection{Liberal}
\textbf{Subscribers:} 66,598 \\
\textbf{Created:} April 2008 \\
\textbf{Description:} A place for liberals to discuss politics, share news, and debate ideas.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{Civility:} Treat all users with respect. Personal attacks, insults, and harassment are not permitted.
    
    \item \textbf{Relevance:} Posts must be relevant to liberalism or liberal politics.
    
    \item \textbf{No Spam:} Spam, self-promotion, and low-quality posts will be removed.
    
    \item \textbf{No Trolling:} Trolling, brigading, and bad-faith participation are not tolerated.
\end{enumerate}

\subsection{Libertarian}
\textbf{Subscribers:} 700,177 \\
\textbf{Created:} August 2008 \\
\textbf{Description:} A place to discuss libertarianism, politics, related topics, and share things that would be of interest to libertarians.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{Follow Reddit's Sitewide Rules:} All Reddit Content Policy rules apply.
    
    \item \textbf{Don't be a dick:} Be respectful in discussion. Personal attacks and harassment are not permitted.
    
    \item \textbf{No spam, advertising, or off-topic:} Posts must be relevant to libertarianism. Spam and advertising are not allowed.
    
    \item \textbf{Advocating for violence is prohibited:} Do not advocate for, threaten, or incite violence.
    
    \item \textbf{No misinformation:} Intentionally spreading false information may result in a ban.
\end{enumerate}

\subsection{mensrights}
\textbf{Subscribers:} 373,697 \\
\textbf{Created:} February 2008 \\
\textbf{Description:} At the most basic level, men's rights are the legal rights that are granted to men. However, any issue that pertains to men's relationship to society is also a topic suitable for this subreddit.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{Posts must be related to men's rights:} All content must be relevant to men's rights or issues affecting men.
    
    \item \textbf{Respect Reddit's rules:} Follow all Reddit sitewide rules and Content Policy.
    
    \item \textbf{Be civil:} Personal attacks, insults, and uncivil behavior are not permitted.
    
    \item \textbf{No spam:} Spam, self-promotion, and low-quality content will be removed.
    
    \item \textbf{No advocating violence:} Do not advocate for, threaten, or incite violence.
    
    \item \textbf{Posts must have proper titles:} Titles should accurately represent the content. No misleading or editorialized titles.
\end{enumerate}

\subsection{PoliticalDiscussion}
\textbf{Subscribers:} 1,096,854 \\
\textbf{Created:} January 2011 \\
\textbf{Description:} A serious subreddit for discussion of political science and current events. Discuss politics, politicians, political theory, political philosophy, political ideology, and current events.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{Keep it civil:} Do not personally insult other users. Attack arguments, not people. Racism, sexism, and other forms of bigotry are not permitted.
    
    \item \textbf{No low investment content:} All posts should include a good-faith attempt to provide discussion-worthy content. Low-effort posts will be removed.
    
    \item \textbf{Post must ask a question:} All submissions must be in the form of a good-faith question about politics or current events.
    
    \item \textbf{Provide context:} Posts must include sufficient context and explanation of the question being asked.
    
    \item \textbf{Do not submit low investment content:} This includes memes, rants, links without commentary, or other low-quality submissions.
    
    \item \textbf{Keep submissions high quality:} All submissions should generate substantive discussion.
    
    \item \textbf{No meta-discussion:} Meta-discussion about Reddit, other subreddits, or this subreddit belongs in the meta thread.
\end{enumerate}

\subsection{progun}
\textbf{Subscribers:} 239,048 \\
\textbf{Created:} November 2010 \\
\textbf{Description:} A subreddit to discuss the political aspects of firearms ownership and related civil liberties.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{Stay on topic:} Posts must be related to the political aspects of firearms and gun rights.
    
    \item \textbf{No personal attacks:} Be civil. Personal attacks and insults are not permitted.
    
    \item \textbf{No anti-gun trolls:} This is a pro-gun subreddit. Anti-gun trolling will result in a ban.
    
    \item \textbf{No spam:} Spam and self-promotion are not allowed without prior moderator approval.
    
    \item \textbf{Quality posts:} Posts should generate substantive discussion about gun rights and politics.
\end{enumerate}

\subsection{racism}
\textbf{Subscribers:} 13,509 \\
\textbf{Created:} June 2008 \\
\textbf{Description:} A place to discuss and learn about racism, its history, and its ongoing impact on society.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{No racism:} Racist content, including racial slurs, stereotypes, and hate speech, will result in an immediate ban.
    
    \item \textbf{Be respectful:} Engage in civil, respectful discussion.
    
    \item \textbf{Stay on topic:} All posts must be related to racism and anti-racism.
    
    \item \textbf{No spam:} Spam and low-quality content will be removed.
    
    \item \textbf{Quality discussion:} Posts should contribute to meaningful discussion about racism.
\end{enumerate}

\subsection{TrueAtheism}
\textbf{Subscribers:} 81,253 \\
\textbf{Created:} February 2012 \\
\textbf{Description:} A subreddit for articulate discussion and news about atheism, theism, and religion.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{Quality:} All posts must meet minimum quality standards. Low-effort posts will be removed.
    
    \item \textbf{Be respectful:} Engage in civil, respectful discussion. Personal attacks are not permitted.
    
    \item \textbf{Substantive content:} Posts should generate substantive discussion about atheism, theism, or religion.
    
    \item \textbf{No preaching:} This is a discussion forum, not a platform for proselytizing.
    
    \item \textbf{Stay on topic:} Posts must be related to atheism, theism, or religion.
\end{enumerate}

\subsection{TrueChristian}
\textbf{Subscribers:} 107,856 \\
\textbf{Created:} October 2012 \\
\textbf{Description:} A subreddit for followers of Jesus Christ. We exist to provide a safe haven for all followers of Jesus Christ to discuss God, Jesus, the Bible, and information relative to our beliefs, and to provide non-believers a place to ask questions about Christianity as explained in the scriptures, without fear of mockery or debasement.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{No profanity:} Profanity and crude language are not permitted.
    
    \item \textbf{Only Christian submissions:} All submissions must be related to Christianity or the Christian life.
    
    \item \textbf{Respect the purpose of this sub:} This is a subreddit for Christians. Respect the community's purpose and beliefs.
    
    \item \textbf{No brigading:} Do not organize or participate in vote brigading or harassment.
    
    \item \textbf{Interactions should be conducive to enriching conversation:} Engage respectfully and constructively. Mockery, belittling, and harassment are not permitted.
    
    \item \textbf{Do not ask for or give money:} Fundraising, donation requests, and financial solicitation are not permitted.
    
    \item \textbf{Approved submissions only:} New accounts and accounts with low karma require moderator approval before posting.
    
    \item \textbf{Surveys require moderator approval:} Contact moderators before posting surveys or research requests.
\end{enumerate}

\subsection{truegaming}
\textbf{Subscribers:} 568,025 \\
\textbf{Created:} September 2010 \\
\textbf{Description:} r/truegaming is a subreddit dedicated to meaningful, insightful, and high-quality discussion on all topics gaming.

\textbf{Account Status:} Banned during experiment.

\subsubsection{Rules}
\begin{enumerate}
    \item \textbf{Posts must promote insightful discussion:} All submissions must be designed to generate thoughtful discussion and avoid low-effort content.
    
    \item \textbf{No off-topic or low-effort content:} Posts must be directly related to gaming and meet quality standards.
    
    \item \textbf{No list posts:} List-based posts (``Top 10 Games'', ``Best RPGs'') are not permitted. Frame discussions around specific questions or analyses.
    
    \item \textbf{Explain your reasoning:} Support your arguments with evidence and explanation. One-line posts or unsupported opinions will be removed.
    
    \item \textbf{No personal attacks:} Be civil and respectful in all interactions.
    
    \item \textbf{No promotion:} Self-promotion, advertising, and spam are not permitted.
    
    \item \textbf{Avoid technical support and ``what should I buy'' questions:} Technical support and purchase advice questions should be directed elsewhere.
\end{enumerate}